\hypertarget{index_proj_desc}{}\section{Project Description}\label{index_proj_desc}
This program allows clients launched from any of 3 machines (acad, mcgonagall, \& csc552) to manipulate the records of a binary-\/encoded dataset stored on the server through the transmission of message packets over a T\-C\-P socket connection. \hypertarget{index_server_desc}{}\section{Server-\/side Description}\label{index_server_desc}
The server accepts incoming client connections, incrementing the number of clients and creating a new process for handling communications for each client. The server contains access to two separate files\-: The binary data file containing data records and a log file that documents all server operations. The server listens for incoming message packets on the socket, performing the corresponding operation for the received command. The server utilizes semaphores to ensure mutual exclusion amongst processes when reading and writing to/from both the dataset and the log file. The server operation is subsequently logged in the log file. \hypertarget{index_client_desc}{}\section{Client-\/side Description}\label{index_client_desc}
On startup, the client will allocate shared memory space and semaphores for all clients, if it is the first client on that machine to run. All subsequent clients on said machine will utilize the existing structures. It will then increment the number of clients in the shared memory space and subsequently find the next available block in the shared memory space, initializing its P\-I\-D and start\-Time fields. The client will utilize semaphores to ensure mutual exclusion amongst processes when reading/writing to the shared memory space and/or the log file. The client is presented with a menu of commands that can be issued to the server and subsequently prompted for their selection. The client will then be prompted for any other necessary information relevant to the command and send it over the socket to the server. All Client operations are then logged in the client log file. The client may perform as many operations as they wish until they specify to exit. \hypertarget{index_readWrite}{}\section{Readers-\/\-Writers Problem}\label{index_readWrite}
The server will utilize a strong writers' preference that allows concurrent reader access for accessing the binary data file. The client will utilize a strong writers' preference that allows concurrent reader access for accessing shared memory. Both the client and the server will utilize a weak reader's preference with concurrent reader access for accessing their log files. \hypertarget{index_menu}{}\section{Menu Options\-:}\label{index_menu}
\hypertarget{index_new_record}{}\subsection{New Record}\label{index_new_record}
Upon selecting the New Record menu option, the client will prompt the user for all necessary fields for a record and validate the user's input. The client will then issue the N\-E\-W command to the server, indicating a new record is to be added, passing it the newly defined record, and awaiting the server's acknowledgment message. \hypertarget{index_display_record}{}\subsection{Display Record}\label{index_display_record}
Upon selecting the Display Record menu option, the client will issue the C\-N\-T command to the server, indicating a request for the number of records, and await the server's response. Upon receiving the number of records, the client will prompt the user for the index of a record between 1 and the received number of records to be displayed, validating the entered value is in that range. The user also has the option to enter -\/999 to display all records. The client will then issue the G\-E\-T command, indicating a request for a particular record or set of records, and await the server's response. The client will then display the received record(s) to the user. \hypertarget{index_change_record}{}\subsection{Change Record}\label{index_change_record}
Upon selecting the Change Record menu option, the client will perform the same operations as Display Record, however, without the option to display all records. After the selected record is displayed, the client will prompt the user to select a field to edit from a menu of editable fields and then prompt the user for a value for that field, reprompting for invalid input if necessary. The client will then issue the F\-I\-X command to the server, indicating a record is to be updated, passing it the newly updated record and its index, and await the server's acknowledgment message. \hypertarget{index_show_log}{}\subsection{Show Server Log}\label{index_show_log}
Upon selecting the Show Log menu option, the client will issue the L\-O\-G command to the server, indicating a request for the contents of the log and await the server's response. The client will receive the number of log records to expect, followed by a stream of individual log records. The client will print each log record to the user as it is received. \hypertarget{index_view_log}{}\subsection{View Client Log}\label{index_view_log}
Upon selecting the View Client Log menu option, the client will access and print the contents of its machine's log file one record a time until it reaches the end of the file. \hypertarget{index_list_clients}{}\subsection{List Local Clients}\label{index_list_clients}
Upon selecting the List Local Clients menu option, the client will access the shared memory and retrieve each of the local client's process I\-Ds one at a time, displaying them to the user 